### 2018-12-04 tex/paper.tex
Included discussion about extension and proof for higher-order potts model

>>>>

\myparagraph{LP-based Submodular Extension} We use the same $1-of-L$ encoding
scheme as for Potts model. In a similar way, problem can be rewritten as

%Same as eq 5.4
\begin{equation}
\min_{{\bf s} \in EP(F)} \quad \sum_{a = 1}^{N} \log \sum_{i = 1}^L \exp(-s_{ai}).
\label{eq:hop_upper_bound}
\end{equation}

Introducing a temperature parameter $T$ to problem (),

%Same as eq 5.5
\begin{equation}
    \min_{{\bf s} \in EP(F)} \quad g_T ({\bf s}) = \sum_{a = 1}^{N} T \cdot \log \sum_{i = 1}^L \exp(-\frac{s_{ai}}{T}).
\label{eq:hop_temp}
\end{equation}

and considering the limit $T \to 0$, problem () becomes

%Same as eq 5.6
\begin{align}
    - \min_{{\bf y} \in \Delta} f({\bf y}) 
\end{align}
where $f(.)$ is the Lovasz extension of $F(.)$. We are interested in making
this LP same as the (), thereby enabling us to recover the submodular extension
for higher-order Potts. The following proposition gives us the submodular
extension.
{\proposition The Lovasz extension of the following submodular extension for
  higher-order Potts model:
  \begin{align}
      F_{HOPotts}(A) &= \sum_a \sum_i \phi_{a}(i) [|A \cap \{v_{ai}\}| = 1] + \nonumber \\
        &\sum_{c \in {\mathcal C}} \max_{(a, b) \in c} \frac{w_c}{2} \sum_{i = 1}^L [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
is the objective function $E({\bf y})$ of the LP relaxation (HOP-LP).
\label{proposition:hop_extension}}
\begin{proof}
  We first observe that $\forall {\bf y} \in {\mathcal L}^N$, that is, for all
  valid labelings, $F_{HOPotts}(A_{\bf y})$ equals $E({\bf y}$.  Hence, $F_{HOPotts}$
    is an extension.

Consider a clique with 3 variables $X_a, X_b, X_c$
each of which can take one of three labels $i = 1, 2, 3$. Then ${\bf x}
= [x_{a1}, x_{a2},x_{a3},x_{b1},x_{b2},x_{b3},x_{c1},x_{c2},x_{c3}]$ is the
vector of relaxed variables. To compute $E({\bf x})$ and $f({\bf x})$, it will
suffice to specify per label ordering. So let us assume $x_{a1} > x_{b1}
> x_{c1}$, $x_{a2} > x_{b2} > x_{c2}$ and $x_{a3} > x_{b3} > x_{c3}$.

Then, the relaxed objective is

\begin{equation}
  E({\bf x}) = \frac{w_c}{2} \cdot [(x_{a1} - x_{c1}) + (x_{a2} - x_{c2}) +(x_{a3} - x_{c3})  ]
\end{equation}

It can be shown that regardless of inter-labeling rankings, the L.E is given
by:

\begin{equation}
  f({\bf x}) = \frac{w_c}{2} \cdot [(x_{a1} - x_{c1}) + (x_{a2} - x_{c2}) +(x_{a3} - x_{c3})  ]
\end{equation}

One can generalise this over more cliques, variables, and labels to show the equivalence of $E({\bf x})$ and $f({\bf x})$.
The Lovasz extension of a set function is convex iff it is submodular. Since $E({\bf x})$
is convex, this implies that $F_{HOPotts}$ is submodular. 
\end{proof}
